% SECCIÓN 1: 
\section{La categoría del testimonio en el contexto actual de la Teología
  Fundamental}



\section{El Valor Cognoscitvo de la Fe y el problema del lenguaje religioso en la
Filosofía Analítica}

Este capítulo sigue el estudio de F. Conesa en Creer y Conocer. En él se
plantean las cuestiones y problemáticas fundamentales relacionadas con el valor
cognoscitivo de la fe en el ámbito de la filosofía analítica.
\textquestiondown{}Cuál es la significatividad del lenguaje religioso? Si se
admite que no carece de significado, \textquestiondown{}Qué valor cognoscitivo
tiene? Si se afirma que es susceptible de ser verdadero o falso
\textquestiondown{}existe un conocimiento religioso? \textquestiondown{}Cuál es
su valor? Esta cuestión nos lleva a la afirmación que estudiaremos en Anscombe:
el valor cognoscitivo de la Fe es el del saber por testimonio.


\section{Significatividad del Lenguaje Religioso}

\section{El Valor Cognoscitivo del Lenguaje Religioso}

Read Knowledge and Certainty: What is operative here is not a
sensible-verification theory, but the picture theory of significant description:
both the proposition and its negation are supposed to describe a possibility,
otherwise the status of the proposition is other than that of a significant
description.

Psychology is no more akin to philosophy than any natural science. Theory of
knowledge is the philosophy of psychology.(4.1121) Wittgenstein and Frege
avoided making theory of knowledge the cardinal theory of philosophy simply by
cutting it dead; by doing none, and concentrating on the philosophy of logic.
But The influence of the tractatus produced logical positivism, whose main
doctrine is verificationism and in that doctrine theory of knowledge reigns
supreme and a prominent position was given to the test for significance by
asking for the observations that would verify a statement.

Wittgenstein's ideas between the Tractatus and the time when he began writing
the Philosophical Investigations were closely akin to logical positivists, less
akin before or after that time.

\section{El Valor Cognoscitivo de la Fe Religiosa}

\section{La Fe como Saber Por Testimonio}
